Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 problem_setting.tex
more edits to abstract, section 2

At each time $t$, a new user (or \emph{agent}) arrives,
whose feature vector (which we also call his \emph{type})
$\AgentV{t} \in \R^d$ is drawn from a known distribution \AgentDist.
Depending on context, we will identify agents with their arrival time
$t$ or their type \AgentV{t}.
When agent $t$ pulls arm $\Pull{t} := i$,
he and all future agents observe a vector
$\ObsV{t} = \ArmV{i} + \NoiseV[t]$ for arm $i$,
and his reward is $\AgentV{t} \cdot \ObsV{t}$,
i.e., agents have linear preferences.
\pfedit{(Although linear, this model permits additional flexibility through the addition of derived attributes that are nonlinear transformation of some original attribute vector: define $\Agent{t}{i} = f_i(\AgentV{t})$ for some known nonlinear functions $f_i$ and $i=d+1,\ldots,d'$, and then increase $d$ to $d'$.)}
\pfcomment{I added some detail.  Is it clear now David?  I'm just talking about a standard trick in linear models, where you add nonlinear transformations of your feature vector and have a linear model in higher dimensions.}

For each time $t$ and arm $i$, let \NumPull{t}{i} be the number of
times that arm $i$ has been pulled (strictly) before time $t$.
An agent at time $t$ estimates arm $i$'s attribute vector as the
average of vectors observed during the arm's past pulls:
$\ArmEV{t}{i} = \frac{1}{\NumPull{t}{i}+1} \cdot
(\ArmEV{0}{i} + \sum_{t'<t: \Pull{t'} = i} \ObsV{t'})$;
here, \ArmEV{0}{i} is a single draw $\ArmV{i} + \NoiseV$ for arm $i$.
(In other words, we assume each arm is pulled once for free at time 0.)
\dkedit{For a justification of the assumption that agents can observe
the actual noisy vectors \ObsV{t'} of past pulls, see
Section~\ref{sec:introduction}.}

@@

We assume above that the distribution $\AgentDist$ over preference
vectors is known to the principal.
In practice, a principal would estimate this distribution from agents'
selections and the attribute estimates and offered payments on which
they were based.
While we do not show it, we hypothesize that our regret guarantees
only change by constants as long as the principal's estimate of the
conditional probability of pulling an arm is correct to within a
constant factor.
\dkdelete{(our algorithm depends on this quantity).}

@@

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV,
breaking ties arbitrarily (but consistently).
\dkedit{Notice that based on Assumption~\ref{A1} below,
  \Best{\AgV} and \Second{\AgV} are unique with probability 1.}

>>>>

At each time $t$, a new user (or \emph{agent}) arrives,
whose feature vector (which we also call his \emph{type})
$\AgentV{t} \in \R^d$ is drawn from a known distribution \AgentDist.
Depending on context, we will identify agents with their arrival time
$t$ or their type \AgentV{t}.
When agent $t$ pulls arm $\Pull{t} := i$,
he and all future agents observe a vector
$\ObsV{t} = \ArmV{i} + \NoiseV[t]$ for arm $i$,
and his reward is $\AgentV{t} \cdot \ObsV{t}$,
i.e., agents have linear preferences.
\pfedit{(Although linear, this model permits additional flexibility through the addition of derived attributes that are nonlinear transformation of some original attribute vector: define $\Agent{t}{i} = \Psi_i(\AgentV{t})$ for some known nonlinear functions $\Psi_i$ where $i=d+1,\ldots,d'$, and then increase $d$ to $d'$.)}
\pfcomment{I added some detail.  Is it clear now David?  I'm just talking about a standard trick in linear models, where you add nonlinear transformations of your feature vector and have a linear model in higher dimensions.}

For each time $t$ and arm $i$, let \NumPull{t}{i} be the number of
times that arm $i$ has been pulled (strictly) before time $t$.
An agent at time $t$ estimates arm $i$'s attribute vector as the
average of vectors observed during the arm's past pulls:
$\ArmEV{t}{i} = \frac{1}{\NumPull{t}{i}+1} \cdot
(\ArmEV{0}{i} + \sum_{t'<t: \Pull{t'} = i} \ObsV{t'})$;
here, \ArmEV{0}{i} is a single draw $\ArmV{i} + \NoiseV$ for arm $i$.
(In other words, we assume each arm is pulled once for free at time 0.)
For a justification of the assumption that agents can observe
the actual noisy vectors \ObsV{t'} of past pulls, see
Section~\ref{sec:introduction}.

@@

We assume above that the distribution $\AgentDist$ over preference
vectors is known to the principal.
In practice, a principal would estimate this distribution from agents'
selections and the attribute estimates and offered payments on which
they were based.
While we do not show it, we hypothesize that our regret guarantees
only change by constants as long as the principal's estimate of the
conditional probability of pulling an arm is correct to within a
constant factor.

@@

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV,
breaking ties arbitrarily (but consistently).
Notice that based on Assumption~\ref{A1} below,
  \Best{\AgV} and \Second{\AgV} are unique with probability 1.
